---
title: "Car_Sales_Analysis"
author: "Jane"
date: "2025-01-27"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

### Importing the Libraries
```{r Importing the libaries, message=FALSE, warning=TRUE}
install.packages("ggplot2")
library(ggplot2)
install.packages("dplyr")
library(dplyr)
install.packages("tidyr")
library(tidyr)
install.packages("reshape")
library(reshape)
```
### Loading the dataset
```{r Loading the dataset}
car_sales_data=read.csv("Car_sales.csv")
head(car_sales_data)
```
### Checking for missing values
```{r Checking for missing values}
head(is.na(car_sales_data))
```
### Removing missing Variable
```{r Removing missing variables}
car_data=na.omit(car_sales_data)
```
### Checking if there are still missing variables
```{r Checking if there are still missing variables}
sum(is.na(car_data))
```
### Checking the Data Structure
```{r Checking Data structure}
str(car_data)
```
### Checking the Latest Launch Column
```{r checking the latest launch column}
class(car_data$Latest_Launch)
head(car_data$Latest_Launch)
```
### Changing the Latest launch format to Date Format
```{r changing to the date format, message=FALSE, warning=TRUE}
install.packages("lubridate")
library(lubridate)
car_data$Latest_Launch <- mdy(car_data$Latest_Launch)
str(car_data)
```
### Grouping the same Manufacturer and then finding the count
```{r Grouping manufacturers}
# Grouping the same Manufacturer and then finding the count
Manufacturer_count <- car_data %>%
  group_by(Manufacturer) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(5)
```
### Print the Manufacturer count
```{r printing the manufacturer count}
print(Manufacturer_count)
```
### Graphically Representing count of Manufacturer using Bar Chart
```{r Graphical representation of Manufacturer count}
ggplot(data = car_data,aes(x=Manufacturer,fill=Manufacturer)) + geom_bar()
```
### Find the top sales of the models in thousands
```{r Top sales of models in thousands}
top_selling_models <- car_data %>%
  arrange(desc(Sales_in_thousands)) %>%
  select(Model, Sales_in_thousands)
```

### Find the top 5 sales of the models in thousands
```{r top 5 sales of models}
top_5_selling_models <- car_data %>%
  arrange(desc(Sales_in_thousands)) %>%
  select(Model, Sales_in_thousands) %>%
  head(5)
```
### Print the top 5 selling models
```{r printing the top 5 selling models}
print(top_5_selling_models)
```
### Visualize the top 5 selling models

### Install and load the dplyr and ggplot2 packages
```{r installing other packages, message=FALSE, warning=TRUE}
install.packages(c("dplyr", "ggplot2"))
library(dplyr)
library(ggplot2)
```

```{r visualization of top 5 selling models}
ggplot(top_5_selling_models, aes(x = reorder(Model, Sales_in_thousands), y = Sales_in_thousands, fill = Model)) +
  geom_col() +
  labs(title = "Top 5 Selling Models", x = "Model", y = "Sales (thousands)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(legend.position = "none") +
  scale_fill_brewer(palette = "Dark2")
```
### Group data by Manufacturer and Model, and calculate total sales
```{r Grouping and calculating the total sales}
top_selling_models <- car_data %>%
  group_by(Manufacturer, Model) %>%
  summarise(total_sales = sum(Sales_in_thousands))
```
### Print the top-selling models
```{r printing the tp selling models}
print(top_selling_models)
```
### Visualize the top-selling models
```{r visualizing the top seliing models}
ggplot(top_selling_models, aes(x = reorder(Model, total_sales), y = total_sales, fill = Manufacturer)) +
  geom_col() +
  labs(title = "Top-Selling Models", x = "Model", y = "Total Sales") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(legend.position = "none")
```
### Scatter plot to visualize the relationship between price and sales.
```{r scatter plot t visualize relationship between price and sales}
ggplot(car_data, aes(x = Price_in_thousands, y = Sales_in_thousands)) +
  geom_point() +
  labs(title = "Price vs Sales", x = "Price (thousands)", y = "Sales (thousands)")
```

### Bar chart to help compare the sales performance of different price segments.
#### Create price segments
```{r Create price segment}
car_data$Price_Segment <- cut(car_data$Price_in_thousands, 
                              breaks = c(0, 20, 40, 60, 80, 100), 
                              labels = c("0-20", "21-40", "41-60", "61-80", "81-100"))
```
#### Group by price segment and calculate total sales
```{r Group and calculate total sales}
price_segment_sales <- car_data %>%
  group_by(Price_Segment) %>%
  summarise(total_sales = sum(Sales_in_thousands))
```
#### The Bar chart
```{r Visulization of price segment}
ggplot(price_segment_sales, aes(x = Price_Segment, y = total_sales, fill = Price_Segment)) +
  geom_col() +
  labs(title = "Sales by Price Segment", x = "Price Segment", y = "Total Sales")
```



